Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

\subsubsection{Finch Logic}
The logical language takes inspiration from relational algebra while incorporating the ordered nature of dimensions in sparse tensors. This means that ev

>>>>

\subsubsection{Finch Logic}
The qulogical language takes inspiration from relational algebra while incorporating the ordered nature of dimensions in sparse tensors. This means that every operator in the language (with the exception of $\finchtable$ which is analagous to the scan operator in RA) takes in an indexed tensor and outputs an indexed tensor. The uniformity of types within this language allows for straightfor
